Program Transformations for miniKanren

### 2020-07-06 papers/aplas/text/evaluation.tex
attempt to compress fig 5

\begin{figure}[!t]
  \centering
  \begin{subfigure}[c]{0.6\textwidth}
    \centering
    \begin{tabular}{c||c|c|c|c}
      & FirstPlain & FirstNando & LastPlain & LastNando \\ \hline\hline
      Original         & 14.8ms     & 14.5ms     & 7.4ms     & 10.1ms    \\ \hline
      \ecce            & 16.0ms     & 22.3ms     & 14.0ms    & 14.9ms    \\ \hline
      ConsPD          & 9.1ms      & 9.7ms      & 9.1ms     & 9.9ms     \\
    \end{tabular}
    \caption{Execution time of evalo}
    \label{tbl:eval}
  \end{subfigure}

  \begin{subfigure}[c]{0.8\textwidth}
    \includegraphics[width=\textwidth]{../data/propEval/prop.pdf}
    \caption{???}
  \end{subfigure}
  \caption{???}
\end{figure}

>>>>

\begin{figure}[!t]
  \centering
  \begin{subfigure}[c]{0.35\textwidth}
    \centering
    %% \begin{tabular}{c||c|c|c|c}
    %%   & FirstPlain & FirstNando & LastPlain & LastNando \\ \hline\hline
    %%   Original         & 14.8ms     & 14.5ms     & 7.4ms     & 10.1ms    \\ \hline
    %%   \ecce            & 16.0ms     & 22.3ms     & 14.0ms    & 14.9ms    \\ \hline
    %%   ConsPD          & 9.1ms      & 9.7ms      & 9.1ms     & 9.9ms     \\
    %% \end{tabular}
    \begin{tabular}{e{1cm}||c|c|c}
      & Original & \ecce & ConsPD \\ \hline\hline
      FirstPlain & 14.8ms & 16.0ms & 9.1ms \\ \hline
      FirstNando & 14.5ms & 22.3ms & 9.7ms \\ \hline
      LastPlain & 7.4ms & 14.0ms & 9.1ms \\ \hline
      LastNando & 10.1ms & 14.9ms & 9.9ms
    \end{tabular}
    \caption{Execution time of evalo}
    \label{tbl:eval}
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{0.6\textwidth}
    \includegraphics[width=\textwidth]{../data/propEval/prop.pdf}
    \caption{???}
  \end{subfigure}
  \caption{???}
\end{figure}
